Flatiron analysis

### 2021-09-10 Rmd/Report 2021.Rmd
update

At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.

@@

```{r drugs episode cleanup}
drugs1 <- drugs %>% 
  filter(episodedatasource == "Administrations" & 
           ismaintenancetherapy == "FALSE") %>%
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  # bind with clinical
  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "months")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "months")) %>% 
  ungroup()

@@

Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded

@@

60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded 
```{r}
remove_60daysrule <- drugs1 %>% 
  filter((days_at_first_drug > 60 | days_at_surg > 60)) %>% 
  distinct(patientid)
remove_60daysrule <- paste(remove_60daysrule$patientid, collapse = "|")

@@

Remove linename that doesn't include platin or taxels -> later, need to recode linenumber first
```{r}
# drugs1 <- drugs1 %>% 
#   # 2. Filtering----
#   filter(episodedatasource == "Administrations" & 
#            # ismaintenancetherapy == "FALSE" & 
#            !is.na(amount) &
#            (days_at_drug < 60 | days_at_surg < 60) &
#            
#            days_at_drug >= 0 &
#            (is.na(surgerydate) | days_at_surg >= 0)
#          )

@@

```{r combine amount same drug one day}
drugs1 <- drugs1 %>% 
  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route,
            diagnosisdate)) %>%

  # 3. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_drug, days_at_surg) %>%
  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  purrr::keep(~!all(is.na(.))) %>%
  ungroup() %>% 
  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>%

@@

Recode linenumber depending on surgery date
```{r line coding}
therapy_line <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>%

@@

# Number of patient who switch line because of surgery from line 1 to adjuvant line
```{r line coding}
therapy_line %>% 
  mutate(change_line = case_when(
    linenumber == 1 & 
      linenumber_new == 2 &
      chemotherapy_type == "Adjuvant" &
      treatment_sequence == "neo + surg + adj"     ~ 1,
    TRUE                                           ~ 0
  )) %>% 
  arrange(desc(change_line)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(change_line) %>% 
  tbl_summary()
```

# How many lines patient got as Neo
```{r}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

@@

# Remove patients with more than 1 line as Neo -34
```{r}
remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1)
remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")

@@

# Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
therapy_line %>% 
  filter(str_detect(linename, "Car") &
           drugname == "cisplatin") %>%
  distinct(patientid) %>% nrow()

@@

@@

# Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>%

@@

When I bind things together I take the closest date of BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. Do we need a max?
Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Calculate bmi
  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
  mutate(bmi_cat = case_when(
    bmi_at_dx < 25                    ~ "Underweight and normal weight",
    bmi_at_dx >= 25 &
      bmi_at_dx < 30                  ~ "Overweight",
    bmi_at_dx >= 30                   ~ "Obese"
  )) %>%
  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
  # Calculate CrCl
  # inner_join(., clinical_data %>% select(-c("diagnosisdate", "surgerydate")),
  #            by = "patientid") %>% 
  mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
  mutate(CrCl = case_when(
    CrCl > 125                        ~ 125,
    TRUE                              ~ CrCl
  )) %>%

@@

# Number of patients
```{r}
Treatment %>% distinct(patientid) %>% nrow()
```

Number of line in neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```
Number of line in Adj neo + surg + adj
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of line in Adj surg + adj
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of line in neo
```{r}
Treatment %>% 
  filter(chemotherapy_type == "Chemotherapy only") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```

# Final dataset
```{r analysis_data}
analysis_data <- Treatment %>% 
  # distinct(patientid, chemotherapy_type, drugname, .keep_all = TRUE) %>% 
  filter(exclude != "1")
```

After excluding exclude == "1" patients, we have `r analysis_data %>% distinct(patientid) %>% nrow()` patients.

@@

>>>>

At this point, after cleaning the clinical data and excluding unfit patients, we have `r nrow(clinical_data)` patients.  
- exclude the patients who had surgery but we don't have a date  
- exclude patients whose histology is unknown  
- exclude patients who didn't survive 1 month

Also height, weight, bsa, creatinine is cleaned and ready. Creatinine minimum is now capped at 0.7 and not 0.8.  
Creatinine clearance maximum is capped at 125.

Now drug cleaning!

@@

**We start with a number of patient who has drug info of `r drugs %>% distinct(patientid) %>% nrow()`.**

## Patients with a date of drug or date of surgery BEFORE diagnosis will be excluded
```{r drugs episode cleanup}
drugs1 <- drugs %>% 
  filter(episodedatasource == "Administrations" & 
           ismaintenancetherapy == "FALSE") %>%
  # 1. 60 days rule between diagnosis and treatment # Loss 1
  # bind with clinical
  inner_join(., clinical_data, #%>% select("patientid", "diagnosisdate", "surgerydate"),
          by = "patientid") %>% 
  arrange(patientid, episodedate) %>% 
  group_by(patientid) %>% 
  mutate(first_drug_date = first(episodedate)) %>% 
  mutate(days_at_first_drug = interval(start = diagnosisdate, end = first_drug_date)/
           duration(n=1, units = "months")) %>% 
  mutate(days_at_surg = interval(start = diagnosisdate, end = surgerydate)/
           duration(n=1, units = "months")) %>% 
  ungroup()

@@

@@

## 60 days rule between diagnosis and treatment
60 days rule between diagnosis and treatment to eliminate patients who didn't get treatment for 60 days which could mean they were treated but it is not recorded 
```{r}
remove_60daysrule <- drugs1 %>% 
  filter((days_at_first_drug > 60 | days_at_surg > 60)) %>% 
  distinct(patientid)
remove_60daysrule <- paste(remove_60daysrule$patientid, collapse = "|")

@@

Remove linename that doesn't include platin or taxels -> later in the process, need first to recode linenumber with all the drugs in.
```{r}
# drugs1 <- drugs1 %>% 
#   # 2. Filtering----
#   filter(episodedatasource == "Administrations" & 
#            # ismaintenancetherapy == "FALSE" & 
#            !is.na(amount) &
#            (days_at_first_drug < 60 | days_at_surg < 60) &
#            
#            days_at_first_drug >= 0 &
#            (is.na(surgerydate) | days_at_surg >= 0)
#          )

@@

## Combine multiple administrations of the same drug at the same date
```{r combine amount same drug one day}
drugs1 <- drugs1 %>% 
  #When want to remove patients who didn't have taxel/platin as 1st line -> remove 260 patients
  # filter(!(linenumber == 1 & !str_detect(linename, "taxel|platin"))) %>% 
  # filter(str_detect(drugname, "taxel|platin") & str_detect(route, "venous|peritoneal")) %>% ############## LATER------------!!!!!
  select(-c(enhancedcohort, episodedatasource, drugcategory, detaileddrugcategory, route)) %>%

  # 3. Combined Multiple Administrations----
  # combined multiple amount of drug given the same day FCF86329BB40C F4E6EE1910940.May be 205 patients row like that
# There are a small number of patients with multiple records in the MedicationAdministration table for the same drug on the same day. We reviewed several instances where this occurs in the original EMR records and found, in each case, legitimate clinical reasons substantiating the multiple administrations per day. Although these instances were legitimate medication administrations, Flatiron Health data are generated from real-world clinical practice and are subject to miscoding and errors by the clinical oncology team, as are all EMR data. Below are three patient vignettes taken from our review of EMR notes, illustrating the variety of reasons why this may occur.
# For clinical reasons, a patient was given higher than normal dose which was listed as two administrations of the normal dose.
# Three administrations of the same drug were listed on a Friday. The EMR note stated that one dose was administered in the office and the patient was sent home with the two remaining doses for the weekend. 
# Patient had an allergic reaction in the past and was administered multiple smaller doses in the same day as part of a desensitization protocol.
  group_by(patientid, linename, linenumber, linestartdate, lineenddate, episodedate, drugname, units, surgerydate, days_at_first_drug, days_at_surg) %>%
  summarise_at(vars(amount), paste, collapse = ";") %>% # don't do sum ti keep the multiple administration in df
  separate(col= amount, paste("amount_", 1:10, sep=""), sep = ";", extra = "warn",
           fill = "right") %>%
  purrr::keep(~!all(is.na(.))) %>%
  ungroup() %>% 
  mutate(amount_1 = as.numeric(amount_1), amount_2 = as.numeric(amount_2),
         amount_3 = as.numeric(amount_3), amount_4 = as.numeric(amount_4)) %>%
  mutate(amount = rowSums(select(.,amount_1:amount_4), na.rm = TRUE)) %>%
  # Found ug, ml, Ea, and NA they are all good, but 
  # ug need conversion
  # the AUC are mostly correct (real mg) but are actual AUC when < at 10 
  mutate(amount =  case_when(
    units == "ug"               ~ amount / 10, # I checked all of them
    units == "AUC" &
      amount < 10               ~ NA_real_,
    TRUE                        ~ amount
  )) %>%

@@

## Recode linenumber depending on surgery date (Categorize Neo and Adjuavnt)
```{r line coding}
therapy_line <- drugs1 %>% 
  # 4. Define Adjuvant, Neoadjuvant, chemo or surgery----
  mutate(chemotherapy_type = case_when(
    # ismaintenancetherapy == "TRUE"    ~ "maintenance",
    episodedate <= surgerydate        ~ "Neoadjuvant", # F63ABD6AEB12C, F4F7B1C5DF24F intraperitoneal Carboplatin
    episodedate > surgerydate         ~ "Adjuvant",
    is.na(surgerydate) &
      !is.na(episodedate)             ~ "Chemotherapy only",
    !is.na(surgerydate) &
      is.na(episodedate)              ~ "Surgery only"
    )) %>% 
  mutate(chemotherapy_type = factor(chemotherapy_type, levels = c("Neoadjuvant", "Adjuvant", "Chemotherapy only", "Surgery only"))) %>%
  group_by(patientid) %>% 
  mutate(had_neo = ifelse(str_detect(chemotherapy_type, "Neo"), "Yes", NA_character_)) %>% 
  fill(had_neo, .direction = "updown") %>% 
  mutate(had_adj = ifelse(str_detect(chemotherapy_type, "Adj"), "Yes", NA_character_)) %>% 
  fill(had_adj, .direction = "updown") %>% 
  mutate(treatment_sequence = case_when(
    had_neo == "Yes" &
      had_adj == "Yes"                           ~ "neo + surg + adj",
    had_neo == "Yes" &
      is.na(had_adj)                             ~ "neo + surg",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "surg + adj",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only"
  )) %>% 
  mutate(therapy = case_when(
    chemotherapy_type == "Neoadjuvant"           ~ "Upfront Chemo",
    chemotherapy_type == "Chemotherapy only"     ~ "Chemotherapy only",
    chemotherapy_type == "Surgery only"          ~ "Surgery only",
    is.na(had_neo) &
      had_adj == "Yes"                           ~ "Upfront Surgery"
  )) %>% 
  fill(therapy, .direction = "downup") %>% 
  # mutate(therapy1 = case_when(
  #   chemotherapy_type == "Adjuvant"              ~ "Upfront Surgery",
  # )) %>% 
  # fill(therapy1, .direction = "downup") %>% 
  # mutate(therapy = coalesce(therapy, therapy1)) %>% 
  # select( -therapy1) %>%

@@

## Number of patient who switch line because of surgery from line 1 to adjuvant line
```{r Number of patient who switch line}
therapy_line %>% 
  mutate(change_line = case_when(
    linenumber == 1 & 
      linenumber_new == 2 &
      chemotherapy_type == "Adjuvant" &
      treatment_sequence == "neo + surg + adj"     ~ 1,
    TRUE                                           ~ 0
  )) %>% 
  arrange(desc(change_line)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(change_line) %>% 
  tbl_summary()
```
## Here I want to plot the lengh of the line 1 which got brought to Adjuvant...

## How many lines patient got as Neo
```{r}
therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()

@@

## Remove patients with more than 1 line as Neo -34
```{r}
remove_morethan1_neo <- therapy_line %>% 
  filter(chemotherapy_type == "Neoadjuvant" &
           linenumber_new != 1)
remove_morethan1_neo <- paste(remove_morethan1_neo$patientid, collapse = "|")

@@

## Remove patients who switch cispl vs carbo # 111 patients Car > Cis F1BF7208F0E96, 34 Cis > Car in neo or adj or chemo
```{r}
# But a lot switch cispl vs carbo # 59 patients Car > Cis F1BF7208F0E96, 32 Cis > Car
therapy_line %>% 
  filter(str_detect(linename, "Car") &
           drugname == "cisplatin") %>%
  distinct(patientid) %>% nrow()

@@

`r emo::ji("question_mark")`

@@

## Code cycle
```{r cycle coding}
# Code cycle number
therapy_cycle <- therapy_line %>%

@@

When I bind things together I take the closest date of creatinine, height, weight, BSA, AUC, from the cycle date to calculate `target_auc` and `expected_dose`. it can be days in between or more. Do we need a max?
Precision when binding for AUC I bind the closest with corresponding drugname (Pacli AUC is not bind with Carbo drug)
```{r target_auc and expected dose}
Treatment <- 
  # Merge with creatinine
  left_join(therapy_cycle, creatinine, by = "patientid") %>%
  mutate(interval_creat = abs(interval(start= creat_date, end= cycle_start_date)/                      
                          duration(n=1, unit="days"))) %>% 
  arrange(interval_creat) %>% 
  distinct(patientid, episodedate, drugname, amount, linenumber_new, cycle_count_perline, cycle_increment, 
           cycle_start_date, .keep_all = TRUE) %>%

@@

  # Calculate bmi
  mutate(bmi_at_dx = weight_at_dx / (height_at_dx * height_at_dx)) %>%
  mutate(bmi_cat = case_when(
    bmi_at_dx < 25                    ~ "Underweight and normal weight",
    bmi_at_dx >= 25 &
      bmi_at_dx < 30                  ~ "Overweight",
    bmi_at_dx >= 30                   ~ "Obese"
  )) %>%
  mutate(bmi_cat = factor(bmi_cat, levels = c("Underweight and normal weight", "Overweight", "Obese"))) %>%
  # Calculate CrCl
  inner_join(., clinical_data %>% select(-surgerydate),
             by = "patientid") %>% 
  mutate(CrCl = ((140 - ageatdx) * weight)/((72 * creatinine) * 0.85)) %>%
  mutate(CrCl = case_when(
    CrCl > 125                        ~ 125,
    TRUE                              ~ CrCl
  )) %>%

@@

## We have `r Treatment %>% distinct(patientid) %>% nrow()` patients with drug and clinical info but

## Exclude exclude == "1" coded by Lauren due to Flatiron rule

```{r analysis_data}
analysis_data <- Treatment %>% 
  filter(exclude != "1")
```

# **Number of patients in almost final dataset is `r analysis_data %>% distinct(patientid) %>% nrow()`**

## Explore the dataset
Number of line in neo
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Neoadjuvant") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```
Number of line in Adj neo + surg + adj
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "neo + surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of line in Adj surg + adj
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Adjuvant" & treatment_sequence == "surg + adj") %>% 
  mutate(n = dense_rank(linenumber_new)) %>% 
  arrange(desc(n)) %>%
  distinct(patientid, .keep_all = TRUE) %>%
  select(n) %>% 
  tbl_summary()
```
Number of line in Chemotherapy only
```{r}
analysis_data %>% 
  filter(chemotherapy_type == "Chemotherapy only") %>% 
  arrange(desc(linenumber_new)) %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  select(linenumber_new) %>% 
  tbl_summary()
```

@@

# STOP HERE
